Simulations

### 2020-12-09 Simulations.Rmd
fix seeding formula
may still be wrong, trying to talk to people who know hockey more

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(ggplot2)
library(plyr)
set.seed(410)
```

@@

# The Model
```{r}
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

@@

  return(rbind(atlantic[1:2,],northeast[1:2,],southeast[1:2,],wildcards[1:2,],wildcards[3:9,]))
}

@@

  return(rbind(central[1:2,],northwest[1:2,],pacific[1:2,],wildcards[1:2,],wildcards[3:9,]))
}

@@

  return(rbind(metro[1:3,],atlantic[1:3,],wildcards[1:2,],wildcards[3:10,]))
}

@@

  return(rbind(central[1:3,],pacific[1:3,],wildcards[1:2,],wildcards[3:8,]))
}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(ggplot2)
library(plyr)
set.seed(400)
```

@@

# The Model
```{r, set.seed(0)}
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

@@

  top8 <- rbind(atlantic[1:2,],northeast[1:2,],southeast[1:2,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:9,]))
}

@@

  top8 <- rbind(central[1:2,],northwest[1:2,],pacific[1:2,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:9,]))
}

@@

  top8 <- rbind(metro[1:3,],atlantic[1:3,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:10,]))
}

@@

  top8 <- rbind(central[1:3,],pacific[1:3,],wildcards[1:2,])
  top8 = top8[order(-top8$totalPoints),]

  return(rbind(top8, wildcards[3:8,]))
}
```
